visitation_bias

### 2021-03-23 code/ms2_bias_niche.Rmd
a new take on ms1 analysis
fixed nomenclature issue

## Generate a data frame that represents visitation and survey abundance
```{r}
# BB visitation data
visitation <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>% # visits per BB-FL pair
  ungroup() %>%
  left_join(pseudodates) %>% # Now we will replace unmatched dates with their pseudo dates
  replace_na(replace = list(mismatch = 0)) %>% # set mismatch to zero for perfectly aligned dates
  filter(mismatch <= 7) %>% # this gets rid of irreconcilable dates (like the t4 dates mentioned above)
  mutate(date2 = if_else(is.na(pseudo.date), date, pseudo.date)) %>% # replace date with pseudodate for all site-dates lacking perfect alignments
  select(-c(date, pseudo.date, mismatch)) %>%
  rename(date = date2) %>%
  group_by(site, date) %>%
  complete(bb.sp, plant.sp, fill = list(visits = 0)) # generate all possible BB-FL combos for each site date and fill in zeros for visits

@@

## 1.2 Binomial multi-level regression models
```{r}
## Exploring the differential bias of bumble bee species and tongue length classes towards floral morphotypes
### Bernoulli with binarized visitation
brm_pvis00 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 | ktype:site), # a varying intercept and slope for ktype:site
                  family = "bernoulli", 
                  file = "../output/brm_pvis_ktype_00",  # for running locally
                  #file = "brm_pvis_ktype_00", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("0", "9", "10")))

brm_pvis01 <- brm(as.integer(visits.bin) ~
                    bb.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype) + # a random intercept and slope for ktype
                    (1 | ktype:site),  # a varying intercept term for ktype:site
                  family = "bernoulli", 
                  file = "../output/brm_pvis_ktype_01",  # for running locally
                  #file = "brm_pvis_ktype_01", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype_pooled, !ktype %in% c("0", "9", "10")))

# If I want to make inference about species visitation rates, I don't need the tongue-length class effect; I just need the site effect. But, when I want to make inference about the tongue length classes, I do need the species-level effect.
brm_pvis02 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 | ktype:site), # a varying intercept and slope for ktype:site
                  family = "bernoulli", 
                  file = "../output/brm_pvis_ktype_02",  # for running locally
                  #file = "brm_pvis_ktype_02", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 5000, # Bulk ESS was a bit low wit 2000 iter
                  data = filter(prop_visits_ktype, !ktype %in% c("0", "9", "10")))
```

## 1.3 Evaluate models
```{r eval=FALSE, include=FALSE}
# Summary
summary(brm_pvis00)
summary(brm_pvis01)
summary(brm_pvis02)

# Posterior predictive checks
pp_check(brm_pvis00)
pp_check(brm_pvis01)
pp_check(brm_pvis02)

# Bayes R2
bayes_R2(brm_pvis00)
bayes_R2(brm_pvis01)
bayes_R2(brm_pvis02)
```

## 1.4 Preliminary visualization
```{r eval=FALSE, include=FALSE}
get_variables(brm_pvis00)
conditional_effects(brm_pvis00)
mcmc_plot(brm_pvis00, pars = c("^r_ktype:tongue.*Intercept]$"))
mcmc_plot(brm_pvis00, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis00, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis00, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis00, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis00, pars = c("^r_ktype:site.*perc.flower.cover]$"))

get_variables(brm_pvis01)
conditional_effects(brm_pvis01)
mcmc_plot(brm_pvis01, pars = c("^r_ktype"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:site.*perc.flower.cover]$"))

get_variables(brm_pvis02)
conditional_effects(brm_pvis02)
mcmc_plot(brm_pvis02, pars = c("^r_ktype"))
mcmc_plot(brm_pvis02, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis01, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis02, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis02, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis02, pars = c("^r_ktype:site.*perc.flower.cover]$"))

get_variables(brm_pvis11)
conditional_effects(brm_pvis11)
mcmc_plot(brm_pvis11, pars = c("^r_ktype:year"))

get_variables(brm_pvis21)
conditional_effects(brm_pvis21)
mcmc_plot(brm_pvis21, pars = c("^r_ktype"))
```

## 1.5 Final visualization
### 1.5.1 morphotype:tongue intercept
```{r}
brm_pvis00_plotframe1 <- brm_pvis00 %>%
  spread_draws(b_Intercept, `r_ktype:tongue`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.tongue = `r_ktype:tongue`) %>% # get rid of the problematic :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype.tongue) %>% # get conditional mean
  group_by(condition) %>% # group by tongue:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = exp(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = exp(.lower),
         .upper_trans = exp(.upper)) %>% 
separate(condition, c("ktype", "tongue"), sep = "_", remove = FALSE) %>% # separate condition term into ktype and tongue
  mutate(ktype = case_when( # rename
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype, levels = c("Disc (1)", "Funnel (2)", # relevel
                                          "Bell (3)", "Stalk-disc (4)", "Lip (5)", 
                                          "Flag (6)", "Head (7)")))

ggplot(brm_pvis00_plotframe1, aes(condition_mean_trans, tongue, 
                                 xmin = .lower_trans, xmax = .upper_trans,
                                 color = tongue, fill = tongue)) +
  geom_pointinterval() +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visitation probability") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(file = "../output/brm_pvis00_plot1.pdf", width = 6, height = 5)
ggsave(file = "../output/brm_pvis00_plot1.png", width = 6, height = 5)
```

### 1.5.2 morphotype:bb.sp intercept
```{r}
brm_pvis02_plotframe2 <- brm_pvis02 %>%
  spread_draws(b_Intercept, `r_ktype:bb.sp`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.bb.sp = `r_ktype:bb.sp`) %>% # get rid of the problematic :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype.bb.sp) %>% # get conditional mean
  group_by(condition) %>% # group by bb.sp:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = inv_logit_scaled(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = inv_logit_scaled(.lower),
         .upper_trans = inv_logit_scaled(.upper)) %>% 
separate(condition, c("ktype", "bb.sp"), sep = "_", remove = FALSE) %>% # separate condition term into ktype and bb.sp
  mutate(ktype = case_when( # rename
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
   mutate(ktype = factor(ktype, levels = c("Disc (1)", "Funnel (2)", # relevel
                                          "Bell (3)", "Stalk-disc (4)", "Lip (5)", 
                                          "Flag (6)", "Head (7)"))) %>%
  left_join(bb_traits) %>%
  mutate(bb.sp = factor(bb.sp, levels = c("telu", "soro", "pyre", "psit", "prat", "lapi", "jone",
                                           "wurf", "pasc", "muci", "mont", "hypn",
                                           "mend", "hort", "gers")))

ggplot(brm_pvis02_plotframe2, aes(condition_mean_trans, bb.sp, 
                                 xmin = .lower_trans, xmax = .upper_trans,
                                 color = pbl.w.class2, fill = pbl.w.class2)) +
  geom_pointinterval() +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visitation probability", y = "Morphotype") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis02_plot1.pdf", width = 8, height = 8)
ggsave(file = "../output/brm_pvis02_plot1.png", width = 8, height = 8)
```

### 1.5.3 morphotype:tongue slope
```{r eval=FALSE, include=FALSE}
brm_pvis00_plotframe3 <- brm_pvis00 %>%
  spread_draws(b_perc.flower.cover, `r_ktype:tongue`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.tongue = `r_ktype:tongue`) %>%
  filter(term == "perc.flower.cover") %>%
  mutate(condition_slope = b_perc.flower.cover + r_ktype.tongue) %>%
  separate(condition, c("ktype", "tongue"), sep = "_", remove = FALSE) %>%
  mutate(ktype = case_when(
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)")))

ggplot(brm_pvis00_plotframe3, aes(condition_slope, tongue, color = tongue)) +
  stat_pointinterval() +
  facet_grid(ktype~.) +
  theme_light() +
  labs(color = "Tongue length", x = "Slope of logit-likelihood") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(file = "../output/brm_pvis00_plot3.png", width = 7, height = 5.5)
```

### 1.5.3 morphotype intercept
```{r}
brm_pvis01_plotframe1 <- brm_pvis01 %>%
  spread_draws(b_Intercept, r_ktype[condition, term]) %>% # the back ticks are necessary to escape the :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype) %>% # get conditional mean
  group_by(condition) %>% # group by tongue:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = inv_logit_scaled(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = inv_logit_scaled(.lower),
         .upper_trans = inv_logit_scaled(.upper)) %>% 
  mutate(ktype = case_when( # rename
    condition == "1" ~ "Disc (1)",
    condition == "2" ~ "Funnel (2)",
    condition == "3" ~ "Bell (3)",
    condition == "4" ~ "Stalk-disc (4)",
    condition == "5" ~ "Lip (5)",
    condition == "6" ~ "Flag (6)",
    condition == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype, levels = c("Head (7)", "Flag (6)", # relevel
                                          "Lip (5)", "Stalk-disc (4)", "Bell (3)", 
                                          "Funnel (2)", "Disc (1)")))

ggplot(brm_pvis01_plotframe1, aes(condition_mean_trans, ktype, 
                                 xmin = .lower_trans, xmax = .upper_trans)) +
  geom_pointinterval() +
  theme_light(16) +
  labs(x = "Visitation probability", y= "Morphotype") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis01_plot1.pdf", width = 6, height = 7)

@@

### 1.5.3 morphotype slope
```{r eval=FALSE, include=FALSE}
brm_pvis01_plotframe2 <- brm_pvis01 %>%
  spread_draws(b_perc.flower.cover, r_ktype[condition, term]) %>% # the back ticks are necessary to escape the :
  filter(term == "perc.flower.cover") %>%
  mutate(condition_slope = b_perc.flower.cover + r_ktype) %>%
  mutate(ktype = case_when(
    condition == "0" ~ "NA (0)",
    condition == "1" ~ "Disc (1)",
    condition == "2" ~ "Funnel (2)",
    condition == "3" ~ "Bell (3)",
    condition == "4" ~ "Stalk-disc (4)",
    condition == "5" ~ "Lip (5)",
    condition == "6" ~ "Flag (6)",
    condition == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)", "NA (0)")))

ggplot(brm_pvis01_plotframe2, aes(condition_slope, ktype)) +
  stat_pointinterval() +
  theme_light() +
  labs(color = "Tongue length", x = "Slope of visitation probability ~ percent flower cover") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis01_plot2.png", width = 7, height = 5.5)
```

@@

# Totally aggregated; note I'm using the full data, not the aligned and trimmed data. No need for complementary floral survey data.
visitation2 <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  filter(!bb.sp %in% c("humi")) %>% # humi is too rare
  #group_by(bb.sp, plant.sp.abb) %>%
  group_by(bb.sp, plant.genus) %>%
  summarize(visits = n()) %>%
  group_by(bb.sp) %>%
  mutate(prop.visits = visits/sum(visits)) %>%
  select(-visits) %>%
  #pivot_wider(names_from = plant.sp.abb, values_from = prop.visits, values_fill = 0) %>%
  pivot_wider(names_from = plant.genus, values_from = prop.visits, values_fill = 0) %>%
  column_to_rownames("bb.sp")

bb_traits2 <- bb_traits %>%
  filter(bb.sp != "humi") %>%
  select(bb.sp, pbl.w.class2) %>%
  arrange(bb.sp) %>%
  mutate(pbl.w.class2.pool = case_when(
    pbl.w.class2 == "short" ~ "short",
    pbl.w.class2 == "med" ~ "med/long",
    pbl.w.class2 == "long" ~ "med/long"
  ))

@@

ggsave("../output/bb_range.pdf", width = 6, height = 5)
```

>>>>

## Generate a data frame that represents visitation and survey abundance
```{r}
# BB visitation data
visitation <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  filter(!bb.sp %in% c("humi", "hypn")) %>% # drop rare species
  group_by(site, date, bb.sp, plant.sp) %>%
  summarize(visits = n()) %>% # visits per BB-FL pair
  ungroup() %>%
  left_join(pseudodates) %>% # Now we will replace unmatched dates with their pseudo dates
  replace_na(replace = list(mismatch = 0)) %>% # set mismatch to zero for perfectly aligned dates
  filter(mismatch <= 7) %>% # this gets rid of irreconcilable dates (like the t4 dates mentioned above)
  mutate(date2 = if_else(is.na(pseudo.date), date, pseudo.date)) %>% # replace date with pseudodate for all site-dates lacking perfect alignments
  select(-c(date, pseudo.date, mismatch)) %>%
  rename(date = date2) %>%
  group_by(site, date) %>%
  complete(bb.sp, plant.sp, fill = list(visits = 0)) # generate all possible BB-FL combos for each site date and fill in zeros for visits

@@

## 1.2 Binomial multi-level regression models
### 1.2.1 Choose priors
```{r}
# For starters, I'm just going to replace the flat prior on the fixed effects we a weakly regularizing prior (on the logit scale)
brm_pvis_prior <- prior(normal(0, 1.5), 
                        class = b) 
```

### 1.2.2 Call models
All these run cleanly.
```{r}
## Exploring the differential bias of bumble bee species and tongue length classes towards floral morphotypes
### Bernoulli with binarized visitation
brm_pvis_00 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 + perc.flower.cover | ktype:tongue) + # a random intercept and slope for ktype:tongue
                    (1 | ktype:site), # a varying intercept and slope for ktype:site
                  family = "bernoulli", 
                  prior = brm_pvis_prior, # weakly regularizing
                  file = "../output/brm_pvis_ktype_00",  # for running locally
                  #file = "brm_pvis_ktype_00", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype, !ktype %in% c("0", "9", "10")))

brm_pvis_01 <- brm(as.integer(visits.bin) ~
                    bb.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype) + # a random intercept and slope for ktype
                    (1 | ktype:site),  # a varying intercept term for ktype:site
                  family = "bernoulli", 
                  prior = brm_pvis_prior, # weakly regularizing
                  file = "../output/brm_pvis_ktype_01",  # for running locally
                  #file = "brm_pvis_ktype_01", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 2000,
                  data = filter(prop_visits_ktype_pooled, !ktype %in% c("0", "9", "10")))

# If I want to make inference about species visitation rates, I don't need the tongue-length class effect; I just need the site effect. But, when I want to make inference about the tongue length classes, I do need the species-level effect.
brm_pvis_02 <- brm(as.integer(visits.bin) ~
                    bb.sp.abund*perc.flower.cover + # fixed term: because more abundant flowers will tend to be more visited,and more abundance bees visit more
                    (1 + perc.flower.cover | ktype:bb.sp) + # a random intercept and random slope for ktype:species; I think I need to model this before I can make conclusions about ktype:pbl.class
                    (1 | ktype:site), # a varying intercept and slope for ktype:site
                  family = "bernoulli", 
                  prior = brm_pvis_prior, # weakly regularizing
                  file = "../output/brm_pvis_ktype_02",  # for running locally
                  #file = "brm_pvis_ktype_02", # for running on the HPC
                  chains = 4,
                  cores = 12,
                  iter = 5000, # Bulk ESS was a bit low wit 2000 iter
                  data = filter(prop_visits_ktype, !ktype %in% c("0", "9", "10")))
```

## 1.3 Evaluate models
```{r eval=FALSE, include=FALSE}
# Summary
summary(brm_pvis_00)
summary(brm_pvis_01)
summary(brm_pvis_02)

# Posterior predictive checks
pp_check(brm_pvis_00)
pp_check(brm_pvis_01)
pp_check(brm_pvis_02)

# MCMC convergence
plot(brm_pvis_00)
plot(brm_pvis_01)
plot(brm_pvis_02)

# Bayes R2
bayes_R2(brm_pvis_00)
bayes_R2(brm_pvis_01)
bayes_R2(brm_pvis_02)
```

## 1.4 Preliminary visualization
```{r eval=FALSE, include=FALSE}
get_variables(brm_pvis_00)
conditional_effects(brm_pvis_00)
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:tongue.*Intercept]$"))
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:tongue.*perc.flower.cover]$"))
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis_00, pars = c("^r_ktype:site.*perc.flower.cover]$"))

get_variables(brm_pvis_01)
conditional_effects(brm_pvis_01)
mcmc_plot(brm_pvis_01, pars = c("^r_ktype*"))
mcmc_plot(brm_pvis_01, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis_01, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis_01, pars = c("^r_ktype:site.*perc.flower.cover]$"))

get_variables(brm_pvis_02)
conditional_effects(brm_pvis_02)
mcmc_plot(brm_pvis_02, pars = c("^r_ktype"))
mcmc_plot(brm_pvis_02, pars = c("^r_ktype:bb.sp.*Intercept]$"))
mcmc_plot(brm_pvis_02, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis_02, pars = c("^r_ktype:bb.sp.*perc.flower.cover]$"))
mcmc_plot(brm_pvis_02, pars = c("^r_ktype:site.*Intercept]$"))
mcmc_plot(brm_pvis_02, pars = c("^r_ktype:site.*perc.flower.cover]$"))
```

## 1.5 Final visualization
### 1.5.1 morphotype:tongue intercept
```{r}
brm_pvis_00_plotframe1 <- brm_pvis_00 %>%
  spread_draws(b_Intercept, `r_ktype:tongue`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.tongue = `r_ktype:tongue`) %>% # get rid of the problematic :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype.tongue) %>% # get conditional mean
  group_by(condition) %>% # group by tongue:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = exp(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = exp(.lower),
         .upper_trans = exp(.upper)) %>% 
separate(condition, c("ktype", "tongue"), sep = "_", remove = FALSE) %>% # separate condition term into ktype and tongue
  mutate(ktype = case_when( # rename
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype, levels = c("Disc (1)", "Funnel (2)", # relevel
                                          "Bell (3)", "Stalk-disc (4)", "Lip (5)", 
                                          "Flag (6)", "Head (7)")))

ggplot(brm_pvis_00_plotframe1, aes(condition_mean_trans, tongue, 
                                 xmin = .lower_trans, xmax = .upper_trans,
                                 color = tongue, fill = tongue)) +
  geom_pointinterval() +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visitation probability") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(file = "../output/brm_pvis_00_plot1.pdf", width = 6, height = 5)
ggsave(file = "../output/brm_pvis_00_plot1.png", width = 6, height = 5)
```

### 1.5.2 morphotype:bb.sp intercept
```{r}
brm_pvis_02_plotframe2 <- brm_pvis_02 %>%
  spread_draws(b_Intercept, `r_ktype:bb.sp`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.bb.sp = `r_ktype:bb.sp`) %>% # get rid of the problematic :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype.bb.sp) %>% # get conditional mean
  group_by(condition) %>% # group by bb.sp:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = inv_logit_scaled(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = inv_logit_scaled(.lower),
         .upper_trans = inv_logit_scaled(.upper)) %>% 
separate(condition, c("ktype", "bb.sp"), sep = "_", remove = FALSE) %>% # separate condition term into ktype and bb.sp
  mutate(ktype = case_when( # rename
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
   mutate(ktype = factor(ktype, levels = c("Disc (1)", "Funnel (2)", # relevel
                                          "Bell (3)", "Stalk-disc (4)", "Lip (5)", 
                                          "Flag (6)", "Head (7)"))) %>%
  left_join(bb_traits) %>%
  mutate(bb.sp = factor(bb.sp, levels = c("telu", "soro", "pyre", "psit", "prat", "lapi", "jone",
                                           "wurf", "pasc", "muci", "mont", "hypn",
                                           "mend", "hort", "gers")))

ggplot(brm_pvis_02_plotframe2, aes(condition_mean_trans, bb.sp, 
                                 xmin = .lower_trans, xmax = .upper_trans,
                                 color = pbl.w.class2, fill = pbl.w.class2)) +
  geom_pointinterval() +
  facet_wrap(~ktype, scales = "free") +
  theme_light() +
  labs(color = "Tongue length", x = "Visitation probability", y = "Morphotype") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis_02_plot1.pdf", width = 8, height = 8)
ggsave(file = "../output/brm_pvis_02_plot1.png", width = 8, height = 8)
```

### 1.5.3 morphotype:tongue slope
```{r eval=FALSE, include=FALSE}
brm_pvis_00_plotframe3 <- brm_pvis_00 %>%
  spread_draws(b_perc.flower.cover, `r_ktype:tongue`[condition, term]) %>% # the back ticks are necessary to escape the :
  rename(r_ktype.tongue = `r_ktype:tongue`) %>%
  filter(term == "perc.flower.cover") %>%
  mutate(condition_slope = b_perc.flower.cover + r_ktype.tongue) %>%
  separate(condition, c("ktype", "tongue"), sep = "_", remove = FALSE) %>%
  mutate(ktype = case_when(
    ktype == "1" ~ "Disc (1)",
    ktype == "2" ~ "Funnel (2)",
    ktype == "3" ~ "Bell (3)",
    ktype == "4" ~ "Stalk-disc (4)",
    ktype == "5" ~ "Lip (5)",
    ktype == "6" ~ "Flag (6)",
    ktype == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)")))

ggplot(brm_pvis_00_plotframe3, aes(condition_slope, tongue, color = tongue)) +
  stat_pointinterval() +
  facet_grid(ktype~.) +
  theme_light() +
  labs(color = "Tongue length", x = "Slope of logit-likelihood") +
  guides(fill = FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggsave(file = "../output/brm_pvis_00_plot3.png", width = 7, height = 5.5)
```

### 1.5.3 morphotype intercept
```{r}
brm_pvis_01_plotframe1 <- brm_pvis_01 %>%
  spread_draws(b_Intercept, r_ktype[condition, term]) %>% # the back ticks are necessary to escape the :
  filter(term == "Intercept") %>% # drop slope terms for now
  mutate(condition_mean = b_Intercept + r_ktype) %>% # get conditional mean
  group_by(condition) %>% # group by tongue:morpotype pair
  point_interval(condition_mean, .width = c(0.95, 0.66)) %>% # calculate credible intervals
  mutate(condition_mean_trans = inv_logit_scaled(condition_mean), # exponentiating the estimates gets us back to the response scale (negbinomial uses log link function)
         .lower_trans = inv_logit_scaled(.lower),
         .upper_trans = inv_logit_scaled(.upper)) %>% 
  mutate(ktype = case_when( # rename
    condition == "1" ~ "Disc (1)",
    condition == "2" ~ "Funnel (2)",
    condition == "3" ~ "Bell (3)",
    condition == "4" ~ "Stalk-disc (4)",
    condition == "5" ~ "Lip (5)",
    condition == "6" ~ "Flag (6)",
    condition == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype, levels = c("Head (7)", "Flag (6)", # relevel
                                          "Lip (5)", "Stalk-disc (4)", "Bell (3)", 
                                          "Funnel (2)", "Disc (1)")))

ggplot(brm_pvis_01_plotframe1, aes(condition_mean_trans, ktype, 
                                 xmin = .lower_trans, xmax = .upper_trans)) +
  geom_pointinterval() +
  theme_light(16) +
  labs(x = "Visitation probability", y= "Morphotype") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis_01_plot1.pdf", width = 6, height = 7)

@@

### 1.5.3 morphotype slope
```{r eval=FALSE, include=FALSE}
brm_pvis_01_plotframe2 <- brm_pvis_01 %>%
  spread_draws(b_perc.flower.cover, r_ktype[condition, term]) %>% # the back ticks are necessary to escape the :
  filter(term == "perc.flower.cover") %>%
  mutate(condition_slope = b_perc.flower.cover + r_ktype) %>%
  mutate(ktype = case_when(
    condition == "0" ~ "NA (0)",
    condition == "1" ~ "Disc (1)",
    condition == "2" ~ "Funnel (2)",
    condition == "3" ~ "Bell (3)",
    condition == "4" ~ "Stalk-disc (4)",
    condition == "5" ~ "Lip (5)",
    condition == "6" ~ "Flag (6)",
    condition == "7" ~ "Head (7)")
  ) %>%
  mutate(ktype = factor(ktype,
                        levels = c("Disc (1)", "Funnel (2)", "Bell (3)", "Stalk-disc (4)",
                                   "Lip (5)", "Flag (6)", "Head (7)", "NA (0)")))

ggplot(brm_pvis_01_plotframe2, aes(condition_slope, ktype)) +
  stat_pointinterval() +
  theme_light() +
  labs(color = "Tongue length", x = "Slope of visitation probability ~ percent flower cover") +
  guides(fill = FALSE)

ggsave(file = "../output/brm_pvis_01_plot2.png", width = 7, height = 5.5)
```

@@

# Totally aggregated; note I'm using the full data, not the aligned and trimmed data. No need for complementary floral survey data.
visitation2 <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male") %>% # we will ignore males 
  filter(!bb.sp %in% c("hypn", "humi")) %>% # hypn and humi are too rare
  #group_by(bb.sp, plant.sp.abb) %>%
  group_by(bb.sp, plant.genus) %>%
  summarize(visits = n()) %>%
  group_by(bb.sp) %>%
  mutate(prop.visits = visits/sum(visits)) %>%
  select(-visits) %>%
  #pivot_wider(names_from = plant.sp.abb, values_from = prop.visits, values_fill = 0) %>%
  pivot_wider(names_from = plant.genus, values_from = prop.visits, values_fill = 0) %>%
  column_to_rownames("bb.sp")

bb_traits2 <- bb_traits %>%
  filter(!bb.sp %in% c("humi", "hypn")) %>% # drop rare species
  select(bb.sp, pbl.w.class2) %>%
  arrange(bb.sp) %>%
  mutate(pbl.w.class2.pool = case_when(
    pbl.w.class2 == "short" ~ "short",
    pbl.w.class2 == "med" ~ "med/long",
    pbl.w.class2 == "long" ~ "med/long"
  ))

@@

ggsave("../output/bb_range_ms2.pdf", width = 6, height = 5)
```

## 3.2 Prep data for calculating niche overlap
```{r}
niche_data <- visitation %>%
  left_join(fl_traits) %>%
  mutate(year = factor(year(date)))
```
